---
title: "exp1_v9v10"
author: "Ruoyu Zhang"
date: "2024-08-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load libraries

```{r}
library(tidyverse)
library(Hmisc)
library(performance)
library(dplyr)
library(readr)
library(afex)
library(stringr)
library(emmeans)
```

# load data from v9

```{r}
df1_v9 <- list.files(path = "/Users/ruoyuzhang/Downloads/Master's Project/data/exp1_v9", full.names = TRUE) %>% 
  lapply(read_csv) %>%
  bind_rows()

demo1_v9 <- read_csv("/Users/ruoyuzhang/Downloads/Master's Project/data/exp1_cf/exp1_cf_v9.csv")
```

# demographic data from v9
## 272 participants in total

```{r}
tidied_demo1_v9 <- demo1_v9 %>%
  select('Question Key', 'Response') %>%
  filter(`Question Key` %in% c("birth.date-year", "sex"))

# gender counts
gender_counts1_v9 <- demo1_v9 %>%
  filter(`Question Key` == "sex") %>%
  group_by(Response) %>%
  summarise(count = n())

print(gender_counts1_v9)

# age counts
age_groups1_v9 <- demo1_v9 %>%
  filter(`Question Key` == "birth.date-year") %>%
  mutate(age = as.numeric(Response)) %>%
  mutate(age_group = cut(age, breaks = seq(0, 100, by = 20), right = FALSE, labels = c("0-19", "20-39", "40-59", "60-79", "80-99"))) %>%
  group_by(age_group) %>%
  summarise(count = n())

print(age_groups1_v9)
```

# data wrangling for exp1 v9

```{r}
tidied_df1_v9 <- df1_v9 %>%
  select("Task Name", "Spreadsheet", "Response") %>%
  filter(!is.na(Response), !Response == "BEGIN", !Response == "END", !Response == "audio started") %>%
  separate("Task Name", into = c("fixation", "modality")) %>%
  separate("Spreadsheet", into = c("duration", "unit"), sep = 3) %>%
  select(-fixation, -unit) %>%
  rename(response = Response) %>%
  transform(duration = as.numeric(duration), response = as.numeric(response))

count1_v9 <- tidied_df1_v9 %>%
  group_by(modality, duration) %>%
  summarise(count = n())

head(tidied_df1_v9)
print(count1_v9)
```

# summary stats for v9

```{r}
summary_stats1_v9 <- tidied_df1_v9 %>%
  group_by(modality, duration) %>%
  summarise(across(response, list(
    mean = ~mean(.),
    sd = ~sd(.),
    lower_ci = ~t.test(.)$conf.int[1],
    upper_ci = ~t.test(.)$conf.int[2]
  ), .names = "{col}_{fn}"))

print(summary_stats1_v9)
```

# filter outliers_2.5SD

```{r}
# Merge the summary statistics back to the original dataframe
tidied_df1_v9_full <- tidied_df1_v9 %>%
  left_join(summary_stats1_v9, by = c("modality", "duration"))

# Filter out data points lying outside of 2.50 SD
filtered_df1_v9 <- tidied_df1_v9_full %>%
  filter(response >= (response_mean - 2.50 * response_sd) & response <= (response_mean + 2.50 * response_sd))

# Count the number of data points in each condition after filtering
count1_filtered_v9 <- filtered_df1_v9 %>%
  group_by(modality, duration) %>%
  summarise(count = n())

# Print the results
head(filtered_df1_v9)
print(count1_filtered_v9)

# some conditions are not meet the minimal amount of participants for a valid result (i.e. at least 26 participants per condition). Therefore, more data collected for specific conditions.
```

# import new data

```{r}
# import
df1_v10 <- list.files(path = "/Users/ruoyuzhang/Downloads/Master's Project/data/exp1_v10", full.names = TRUE) %>% 
  lapply(read_csv) %>%
  bind_rows()

demo1_v10 <- read_csv("/Users/ruoyuzhang/Downloads/Master's Project/data/exp1_cf/exp1_cf_v10.csv")
```

# demographic data from v10
## 19 more participants (7  for 438ms audio, 12  for 752ms audio)

```{r}
tidied_demo1_v10 <- demo1_v10 %>%
  select('Question Key', 'Response') %>%
  filter(`Question Key` %in% c("birth.date-year", "sex"))

# gender counts
gender_counts1_v10 <- demo1_v10 %>%
  filter(`Question Key` == "sex") %>%
  group_by(Response) %>%
  summarise(count = n())

print(gender_counts1_v10)

# age counts
age_groups1_v10 <- demo1_v10 %>%
  filter(`Question Key` == "birth.date-year") %>%
  mutate(age = as.numeric(Response)) %>%
  mutate(age_group = cut(age, breaks = seq(0, 100, by = 20), right = FALSE, labels = c("0-19", "20-39", "40-59", "60-79", "80-99"))) %>%
  group_by(age_group) %>%
  summarise(count = n())

print(age_groups1_v10)
```

# data wrangling for exp1 v10

```{r}
tidied_df1_v10 <- df1_v10 %>%
  select("Task Name", "Spreadsheet", "Response") %>%
  filter(!is.na(Response), !Response == "BEGIN", !Response == "END", !Response == "audio started") %>%
  separate("Task Name", into = c("fixation", "modality")) %>%
  separate("Spreadsheet", into = c("duration", "unit"), sep = 3) %>%
  select(-fixation, -unit) %>%
  rename(response = Response) %>%
  transform(duration = as.numeric(duration), response = as.numeric(response))

count1_v10 <- tidied_df1_v10 %>%
  group_by(modality, duration) %>%
  summarise(count = n())

head(tidied_df1_v10)
print(count1_v10)
```

# summary stats for exp1 v10

```{r}
summary_stats1_v10 <- tidied_df1_v10 %>%
  group_by(modality, duration) %>%
  summarise(across(response, list(
    mean = ~mean(.),
    sd = ~sd(.),
    lower_ci = ~t.test(.)$conf.int[1],
    upper_ci = ~t.test(.)$conf.int[2]
  ), .names = "{col}_{fn}"))

print(summary_stats1_v10)
```

# merge v10 into the original data frame

```{r}
# first make sure all columns are the same
tidied_df1_v10_full <- tidied_df1_v10 %>%
  left_join(summary_stats1_v10, by = c("modality", "duration"))

# bind rows
df1_new <- bind_rows(tidied_df1_v9_full, tidied_df1_v10_full)
```

# calculate the new summary stats

```{r}
summary_stats1_new <- df1_new %>%
  group_by(modality, duration) %>%
  summarise(across(response, list(
    mean = ~mean(.),
    sd = ~sd(.),
    lower_ci = ~t.test(.)$conf.int[1],
    upper_ci = ~t.test(.)$conf.int[2]
  ), .names = "{col}_{fn}"))

count1_new <- df1_new %>%
  group_by(modality, duration) %>%
  summarise(count = n())

print(summary_stats1_new)
print(count1_new)
```

# plot for summary stats

```{r}
ggplot(summary_stats1_new, aes(x = duration, y = response_mean, color = modality, group = modality)) +
  geom_line() +
  geom_point() +
  labs(title = "Mean Response by Modality and Duration",
       x = "Duration",
       y = "Mean Response") +
  theme_minimal()


df1_new %>%
  ggplot(aes(x = duration, y = response, color = modality)) +
  geom_point() +
  geom_jitter() +
  geom_smooth(method = "lm", se = FALSE) +
  theme_minimal() +
  theme(text = element_text(size = 13)) +
  labs(x = "durations",
       y = "response")
```

# inferential statistics

```{r}
# fit a model
m.interaction1 <- lm(response ~ modality*duration, data = df1_new)
anova(m.interaction1)

# Assumption check
# Residual diagnostic plots
par(mfrow = c(2, 2))
plot(m.interaction1)
# Shapiro-Wilk test for normality
shapiro.test(residuals(m.interaction1))

# Display the model coefficients
summary(m.interaction1)$coefficients

# Obtain slopes
m.lst1 <- lstrends(m.interaction1, "modality", var = "duration")
m.lst1
# Compare slopes
pairs(m.lst1)


# Obtain intercepts
emm1 <- emmeans(m.interaction1, ~ modality)
emm1
# Perform pairwise comparisons of the intercepts
pairs(emm1)
```









